---
title: "ACN4"
author: "Eric Zhao"
date: "2023-09-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Parameters set-up
```{r}
# Clearing the workspace (equivalent to MATLAB's "clear all")
rm(list=ls())

# Setting up parameters (translated from MATLAB to R)
T <- 400  # stop time T
pX <- 0.01  # probability of speciation for X species (e.g., plant)
pY <- 0.01  # probability of speciation for Y species (e.g., animal)
maxNX <- 500  # maximum number of X species for preallocation
maxNY <- 1500  # maximum number of Y species for preallocation
v <- 1  # tolerance parameter for trait matching
theta <- 0.1  # assuming all theta values are the same in the model
thetax <- theta #phenotypic variance for x,
thetay <- theta #phenotypic variance for y,
xix <- 0.1  # standard deviation for drift (X species)
xiy <- 0.1  # standard deviation for drift (Y species)
xis <- 0.5  # standard deviation for trait value change during speciation
c <- 0.99  # proportion of connection probability based on historical association

```

## Other Initializations
```{r}
# Initializations

# Starting with a single mutualism

# Trait values
x<-matrix(0, nrow=2, ncol=maxNX)
xall <- matrix(0, nrow=T, ncol=maxNX)
y<-matrix(0, nrow = 2, ncol = maxNY)
yall <- matrix(0, nrow=T, ncol=maxNY)

# Initial trait values
x[1,1] <- 0
y[1,1] <- 0

# Interaction matrix (1 if species i and j interact, 0 otherwise)
A <- matrix(0, nrow=1, ncol=1)
# We start with one species each that are connected to each other
A[1,1] <- 1

NsppX = 1; # total # of species of type X that have ever existed
iXextant = 1;  #the indicies of the extant species (out of the NsppX in x)

NsppY = 1; # total # of species of type X that have ever existed
iYextant = 1;  #the indicies of the extant species (out of the NsppX in x)

# List to keep track of extinct species
#total # of extant species 
NextantsppX <- length(iXextant)
NextantsppY <- length(iYextant)

#keep track of phylogeny using indexing pointer--The
#first row holds the tree topology and the second row holds the metric of
#the tree (what generation speciation occured)
phylogenyX<-matrix(0, nrow = 2, ncol = NsppX)
phylogenyX<-rbind(c(1, 0), c(2, 0))
phylogenyY<-matrix(0, nrow = 2, ncol = NsppY)
phylogenyY<-rbind(c(1, 0), c(2, 0))


connectedness <- matrix(0, 1, T)
connectX <- matrix(0, 1, T)
connectY <- matrix(0, 1, T)

# creating a list storing interaction matrix at each time stamp
ts_list<-list()
```

## Simulation Loop
```{r}
# Main simulation loop
for (n in 1:T) {
    # Drift in traits for existing species
    xall[n,] <- x[1, ] 
    yall[n,] <- y[1, ] 
    
    #average trait value of the interactors with any
    #particular species
    if(is.matrix(A)){
      AvgXconnection<-A %*% as.matrix(y[1, iYextant])/as.matrix(rowSums(A))
      AvgYconnection<-t(A) %*% as.matrix(x[1, iXextant])/as.matrix(colSums(A))
    }
    
    else{
      AvgXconnection <- A * y[1, iYextant]
      AvgYconnection <- A * x[1, iXextant]
    }
    Aold <- A
    
    muI<-AvgXconnection
    muJ<-AvgYconnection
    
    w<-A
    for (i in 1:NextantsppX) {
    if(is.matrix(A)){
    nI <- sum(A[i,])
    }
    else{nI <-sum(A)}
    for (j in 1:NextantsppY) {
      if(is.matrix(A)){
        mJ <- sum(A[,j])
      }
      else{mJ<- sum(A)}
      
    numerator1 <- (theta + v) / (mJ * sqrt(theta^2 + theta * v + v^2))
    numerator2 <- (theta + v) / (nI * sqrt(theta^2 + theta * v + v^2))
        
    expTerm1 <- -1 * (v * (x[1, iXextant[i]] - muJ[j]) * (x[1, iXextant[i]] + muJ[j] - 2 * muI[i]) + theta * (muI[i] - muJ[j]) * (muI[i] + muJ[j] - 2 * x[1, iXextant[i]]))
    expTerm2 <- -1 * (v * (y[1, iYextant[j]] - muI[i]) * (y[1, iYextant[j]] + muI[i] - 2 * muJ[j]) + theta * (muJ[j] - muI[i]) * (muI[i] + muJ[j] - 2 * y[1, iYextant[j]]))
        
    denominator <- theta^2 + theta * v + v^2
        
    #w[i,j] <- numerator1 * exp(expTerm1 / denominator)
    if(is.matrix(w)){
    w[i,j] <- numerator2 * exp(expTerm2 / denominator)
        }
    else{w<-numerator2 * exp(expTerm2 / denominator)}
      }
  }
    
    

m<-0
NoldsppX <- NsppX

for (i in iXextant) {  # only look at the extant species
                       # i is the index of each of the extant of individuals/species
                       # recall we need to put NaN where spec have gone extinct, not
                       # delete them completely, so this limits us to only calling extant
                       # species to speciate and evolve
  
  m <- m + 1  # counts which species we are on to use as an index for iXextant, A
              # where i acts as an index for x, i.e iXextant[m] = i

  # variation from one generation to the next
  if(is.matrix(Aold)){
  nI <- sum(Aold[m,])
  }
  else{nI<-sum(Aold)}
  thetaI <- thetay / nI  # CLT
  
  alpha <- (thetaI^2 + thetaI*v + v^2) / (thetaI^2 + thetaI*v + v^2 + thetax*v)
  gamma1 <- thetaI * thetax / (thetaI^2 + thetaI*v + v^2 + thetax*v)
  
  if(is.matrix(Aold)){
  non_zero_indices <- which(Aold[m,] != 0)
  x[2, i] <- alpha * x[1, i] + (1 - alpha) * AvgXconnection[m] + (AvgXconnection[m] - mean(AvgYconnection[non_zero_indices])) * gamma1 + rnorm(1) * xix
  }
  else{
     x[2, i] <- alpha * x[1, i] + (1 - alpha) * AvgXconnection[m] + (AvgXconnection[m] - mean(AvgYconnection)) * gamma1 + rnorm(1) * xix
  }




# speciation event - which occurs with probability pX
  if (runif(1) < pX) {
    NsppX <- NsppX + 1  # keeps track of how many spp there are now
    
    if (NsppX > maxNX) {
        cat("error, the number of species type X is greater than the number allocated\n")
        toobig <- toobig + 1
        break
    }
    
    # add new spp trait
    x[2, NsppX] <- x[1, i] + rnorm(1) * xis
    if(is.matrix(A)){
    A <- rbind(A, A[m, ])  # inherits parental connections
    w <- rbind(w, w[m, ])  # and those connections inherit the same fitness value, at least initially
    }
    # else{
    #    A<-rbind(A, A[m])
    #    w<-rbind(w, w[m])
    #  }
    # now we make sure that we know that this new species is a sister species to species i
    boo <- which(phylogenyX[1, ] == i)
  if((NsppX-1)>=(boo[1]+1)){
    for (j in (NsppX-1):(boo[1]+1)) {
        phylogenyX <- cbind(phylogenyX,phylogenyX[, j])
    }
  }
    if((boo[1]+1)<=dim(phylogenyX)[2]){
    phylogenyX[, boo[1]+1] <- c(NsppX, n)
    }
    else{phylogenyX<-cbind(phylogenyX, c(NsppX, n))}
}

    
}   

   m <- 0
   NoldsppY <- NsppY

for (i in iYextant) {

  m <- m + 1; #counts which species we are on
  if(is.matrix(Aold)){
  mJ<- sum(Aold[,m])
  }
  else{mJ<-sum(Aold)}
  thetaJ <- thetax / mJ  # CLT
  
  beta <- (thetaJ^2 + thetaJ*v + v^2) / (thetaJ^2 + thetaJ*v + v^2 + thetay*v)
  gamma2 <- thetaJ * thetax / (thetaJ^2 + thetaJ*v + v^2 + thetay*v)
  
  if(is.matrix(Aold)){
  non_zero_indices <- which(Aold[,m] != 0)
    y[2, i] <- beta * y[1, i] + (1 - beta) * AvgYconnection[m] + (AvgYconnection[m] - mean(AvgXconnection[non_zero_indices])) * gamma2 + rnorm(1) * xix
  }
  else{
    y[2, i] <- beta * y[1, i] + (1 - beta) * AvgYconnection[m] + (AvgYconnection[m] - mean(AvgXconnection)) * gamma2 + rnorm(1) * xix
  }



# speciation event - which occurs with probability pY
  if (runif(1) < pY) {
    NsppY <- NsppY + 1  # keeps track of how many spp there are now
    
    if (NsppY > maxNY) {
        cat("error, the number of species type X is greater than the number allocated\n")
        toobig <- toobig + 1
        break
    }
    
    # add new spp trait
    y[2, NsppY] <- y[1, i] + rnorm(1) * xis
    if(is.matrix(A)){
    A <- cbind(A, A[, m])  # inherits parental connections
    w <- cbind(w, w[, m])  # and those connections inherit the same fitness value, at least initially
    }
    # else{
    #    A<-rbind(A, A[m])
    #    w<-rbind(w, w[m])
    #  }
    # now we make sure that we know that this new species is a sister species to species i
    boo <- which(phylogenyY[1, ] == i)
  if((NsppY-1)>=boo[1]){
    for (j in (NsppY-1):boo[1]) {
        phylogenyY <- cbind(phylogenyY,phylogenyY[, j])
          }
    }
    if((boo[1]+1)<=dim(phylogenyY)[2]){
    phylogenyY[, boo[1]+1] <- c(NsppY, n)
    }
    else{phylogenyY<-cbind(phylogenyY, c(NsppY, n))}
}

}
   
#interaction matrix - these are in the order in which spp appeared, but not including extinct species 
count<-1
im<-0
jm<-0

if((NoldsppX+1)<=NsppX){
iXextantnew <- c(iXextant,(NoldsppX+1):NsppX)#give the linages of X that are extant
} 
else{iXextantnew<-iXextant}
if((NoldsppY+1)<=NsppY){
iYextantnew <- c(iYextant,(NoldsppY+1):NsppY) #give the linages of Y that are extant
}
else{iYextantnew<-iYextant}
Anew <- matrix(0, length(iXextantnew),length(iYextantnew))

for (i in iXextantnew) {
  im<-im+1
  for (j in iYextantnew) {
  jm<-jm+1
   if(is.matrix(A)){
  matching <- c*A[im,jm]+ (1-c)*w[im,jm]
  }
   else{
  matching <- c*A+ (1-c)*w
  }
   if(matching>runif(1)){
    Anew[im, jm]<-1
  }
  }
  jm<-0
}

# Identify extant species with connections
XextantA <- which(rowSums(Anew) != 0)
iXextant <- iXextantnew[XextantA]
NextantsppX <- length(iXextant)

YextantA <- which(colSums(Anew) != 0)
iYextant <- iYextantnew[YextantA]
NextantsppY <- length(iYextant)

# Check for extinction of species
if (NsppX == 0 && NsppY == 0) {
    cat("extinction of both species\n")
    extinctions <- extinctions + 1
    next # replaces MATLAB's break in this context
} else if (NsppX == 0) {
    cat("extinction of species X\n")
    extinctions <- extinctions + 1
    next
} else if (NsppY == 0) {
    cat("extinction of species Y\n")
    extinctions <- extinctions + 1
    next
}

# Update interaction matrix
A <- Anew[XextantA, YextantA]

# Update traits for next generation
x[1, ] <- x[2, ]
x[2, ] <- rep(NaN, maxNX)
y[1, ] <- y[2, ]
y[2, ] <- rep(NaN, maxNY)

# Calculate connectedness
connectedness[1, n] <- sum(sum(A)) / (NextantsppX * NextantsppY)
# connectX[1, n] <- mean(rowSums(A)) / NextantsppY
# connectY[1, n] <- mean(colSums(A)) / NextantsppX

## appending new interaction matrix into the list

ts_list[[n]]<-A
   
   
}
```


```{r Packages, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Store string containing all required packages
my_packages <- c('bipartite', 'RColorBrewer', 'igraph')

# Store all installed packages
ya_loaded <- (.packages())

# Check whether required packages are already installed and grab only those that still need installation
need_load<-my_packages[!(my_packages %in% ya_loaded)]

# Load required packages
lapply(need_load, require, character.only = TRUE)
```


``` {r}
# assign plants' name to the plants
rname_vec<-rep(0, length(A[,1]))
for (i in 1:length(A[,1])) {
  rname_vec[i]<-paste("PL",i,sep = "")
}
row.names(A)<-rname_vec

cname_vec<-rep(0, length(A[1,]))
for (i in 1:length(A[1,])) {
  cname_vec[i]<-paste("V",i,sep = "")
}
row.names(A)<-rname_vec
colnames(A)<-cname_vec
# view the new matrix
View(A)

```

## Analyze bipartite graphs at a fixed time

### First convert adjacency matrix to edgelist
```{r}
#
polli.g<- graph.incidence(as.matrix(A), weighted = TRUE)
polli_el <- get.edgelist(polli.g)
View(polli_el)
```



### Structuring the bipartite graphs
```{r}
# Set the arbitrary char as webID 
webID <- data.frame(matrix("pp", nrow = nrow(polli_el), ncol = 1))
polli_new <- cbind(polli_el, webID)
# assign column names
colnames(polli_new)<- c("plant", "pollinator", "webID")
View(polli_new)
```



### Plotting network interactions between two node types
```{r}
#Generate the network matrix in bipartite
polli_web<- frame2webs(polli_new, varnames = c("plant", "pollinator", "webID"), type.out = "list", emptylist = TRUE)
# create a color vector
cols1<-c( '#8214a0', '#005ac8', '#00a0fa', '#fa78fa', '#14d2dc', '#aa0a3c', '#fa7850', '#0ab45a', '#f0f032', '#a0fa82', '#fae6be') 
# plot the two-dimensional matrix to a bipartite graph
plotweb(polli_web$"pp", method='cca', labsize=1,col.interaction=cols1, bor.col.interaction=cols1)                    
```




### Visualizing the interaction matrix
This code will visualize the interaction/adjacency matrix. Look up the documentation, play with the command, and then comment within the code block to explain how to use visweb.

``` {r}
# set the color of levels of interactions
cols2<-c('white', '#006e82')
#you can also try other palettes
#cols2 <- brewer.pal(2, "Reds")
#visualize the interaction matrix
visweb(polli_web$'pp', type='nested', labsize=0.3, plotsize=28 ,square="def",def.col=cols2)
```



## Visualization
```{r}

# Plot the evolution of species traits over time for X and Y
par(mfrow=c(3,2))  # Set up a 3x2 plotting grid

plot(1:T, xall[1:T,1], type="p", cex=0.5, ylab="Mean Trait x", main="Evolution of Species Trait X")
plot(1:T, yall[1:T,1], type="p", cex=0.5, ylab="Mean Trait y", main="Evolution of Species Trait Y")


# Display the adjacency matrix of interactions(this is t=400)
x.at<-seq(0, NsppX+1)
y.at<-seq(0, NsppY+1)
image(t(A[1:NsppX, 1:NsppY]), axes=FALSE, main="Adjacency Matrix of Interactions", xlab="Pollinator species", ylab="Plant species")
axis(1, at=x.at)
axis(2, at=y.at)

             
# Display the distribution of connections per pollinator
hist(rowSums(A[1:NsppX, 1:NsppY]), main="Distribution of Connections per Pollinator", xlab="Number of connections", ylab="Frequency") 

# Display connectedness over time
plot(1:T, connectedness, type="l", ylab="Connectedness", xlab="Iterations", main="Connectedness Over Time")

```
## time-evolving networks
```{r}
#largest dimension
max_dim<-unlist(lapply(ts_list, dim))[c(n*2-1, n*2)]
#building a multidimensional array with with incomplete entries
ts_list_expanded<-list()
for (i in 1:n) {
  new_mat<-matrix(NA,nrow=max_dim[1],ncol=max_dim[2])
  new_mat[1:nrow(ts_list[[i]]), 1:ncol(ts_list[[i]])] <- ts_list[[i]]
  ts_list_expanded[[i]]<-new_mat
}
ts_multi_A<-array(c(unlist(ts_list_expanded)), dim = c(21, 7, n))
```


## ...
```{r}

```






