---
title: "ACN4+"
author: "Eric Zhao，Carrie Diaz Eaton"
date: "2023-10-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Packages, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Store string containing all required packages
my_packages <- c('keep','bipartite', 'RColorBrewer', 'igraph')

# Store all installed packages
ya_loaded <- (.packages())

# Check whether required packages are already installed and grab only those that still need installation
need_load<-my_packages[!(my_packages %in% ya_loaded)]

# Load required packages
lapply(need_load, require, character.only = TRUE)
```

# Stochastic Asymmetric Co-evolving Network Model

## Parameters set-up
```{r}
# Clearing the workspace (equivalent to MATLAB's "clear all")
rm(list=ls())

# Setting up parameters (translated from MATLAB to R)
T <- 600  # stop time T
pX <- 0.01  # probability of speciation for X species (e.g., plant)
pY <- 0.01  # probability of speciation for Y species (e.g., animal)
maxNX <- 500  # maximum number of X species for preallocation
maxNY <- 1500  # maximum number of Y species for preallocation
v <- 1  # tolerance parameter for trait matching
theta <- 0.1  # assuming all theta values are the same in the model
thetax <- theta #phenotypic variance for x,
thetay <- theta #phenotypic variance for y,
xix <- 0.1  # standard deviation for drift (X species)
xiy <- 0.1  # standard deviation for drift (Y species)
xis <- 0.5  # standard deviation for trait value change during speciation
c <- 0.9  # proportion of connection probability based on historical association

#other counters
extinctions <-0 #count full network extinctions
Xextinctions<-0 #count X extinctions
Yextinctions<-0 #count Y extinctions
toobig <-0
```

## Other Initializations
```{r}
# Initializations

# Starting with a single mutualism


# creating a list storing interaction matrix at each time stamp
s_size<-10
ts_list<-vector(mode = "list", length = s_size)
ts_stats_list<-vector(mode = "list", length = s_size)
modu_scores_list<-vector(mode = "list", length = s_size)

ts_stats<-matrix(0, nrow = 10, ncol = T)

iteration_times<-rep(NA, T)
inter_event_times<-c()
last_event_time<-0

```

## Simulations
```{r, warning=FALSE}
for(k in 1:s_size){
  
  
# Trait values
x<-karray(0, c(2, maxNX))
xall <- karray(0, c(T, maxNX))
y<-karray(0, c(2, maxNY))
yall <- karray(0, c(T, maxNY))


# Initial trait values
x[1,1] <- 0
y[1,1] <- 0

# Interaction matrix (1 if species i and j interact, 0 otherwise)
A <- matrix(0, nrow=1, ncol=1)
M <- matrix(0, nrow=1, ncol=1)
# We start with one species each that are connected to each other
A[1,1] <- 1
M[1,1] <- 0
NsppX = 1; # total # of species of type X that have ever existed
iXextant = 1;  #the indicies of the extant species (out of the NsppX in x)

NsppY = 1; # total # of species of type X that have ever existed
iYextant = 1;  #the indicies of the extant species (out of the NsppX in x)

# List to keep track of extinct species
#total # of extant species 
NextantsppX <- length(iXextant)
NextantsppY <- length(iYextant)

#keep track of phylogeny using indexing pointer--The
#first row holds the tree topology and the second row holds the metric of
#the tree (what generation speciation occured)
# phylogenyX<-matrix(0, nrow = 2, ncol = NsppX)
# phylogenyX<-rbind(c(1, 0), c(2, 0))
# phylogenyY<-matrix(0, nrow = 2, ncol = NsppY)
# phylogenyY<-rbind(c(1, 0), c(2, 0))


connectedness <- matrix(0, 1, T)
connectX <- matrix(0, 1, T)
connectY <- matrix(0, 1, T)

modu_scores<-c()

# Main simulation loop
for (n in 1:T) {
  start_time<-Sys.time()
  # Drift in traits for existing species
  xall[n,] <- x[1, ] 
  yall[n,] <- y[1, ] 
    
  Yextant <- karray(y[1, iYextant], c(1,NextantsppY)) #trait values of extant only
  AvgXconnection<-A %*% t(Yextant)/rowSums(A)
  muI <- karray(AvgXconnection, c(NextantsppX,1))
  
  Xextant <- karray(x[1, iXextant], c(NextantsppX,1))
  AvgYconnection<-t(A) %*% Xextant/rowSums(t(A))
  muJ <- karray(AvgYconnection, c(NextantsppY,1))

  #updates
  Aold <- A
  w<-A
  
  for (i in 1:NextantsppX) {
    
    nI <- sum(A[i,])
  
   
  for (j in 1:NextantsppY) {
    
    mJ <- sum(A[,j])
  
    numerator1 <- (theta + v) / (mJ * sqrt(theta^2 + theta * v + v^2))
    numerator2 <- (theta + v) / (nI * sqrt(theta^2 + theta * v + v^2))
      
    expTerm1 <- -1 * (v * (x[1, iXextant[i]] - muJ[j]) * (x[1, iXextant[i]] + muJ[j] - 2 * muI[i]) + theta * (muI[i] - muJ[j]) * (muI[i] + muJ[j] - 2 * x[1, iXextant[i]]))
    expTerm2 <- -1 * (v * (y[1, iYextant[j]] - muI[i]) * (y[1, iYextant[j]] + muI[i] - 2 * muJ[j]) + theta * (muJ[j] - muI[i]) * (muI[i] + muJ[j] - 2 * y[1, iYextant[j]]))
      
    denominator <- theta^2 + theta * v + v^2
      
    #w[i,j] <- numerator1 * exp(expTerm1 / denominator)
    w[i,j] <- numerator2 * exp(expTerm2 / denominator)
    M[i,j] <-w[i,j]/sum(w[i,]) #normalized to probabilites

  }
}
  m<-0
  NoldsppX <- NsppX
  
  # only look at the extant species
  # i is the index of each of the extant of individuals/species
  # recall we need to put NaN where spec have gone extinct, not
  # delete them completely, so this limits us to only calling extant
  # species to speciate and evolve
  for (i in iXextant) {
    m <- m + 1  # counts which species we are on to use as an index for iXextant, A
    # where i acts as an index for x, i.e iXextant[m] = i
    
    # variation from one generation to the next
    nI <- sum(Aold[m,])
    
    thetaI <- thetay / nI  # CLT
    
    alpha <- (thetaI^2 + thetaI*v + v^2) / (thetaI^2 + thetaI*v + v^2 + thetax*v)
    gamma1 <- thetaI * thetax / (thetaI^2 + thetaI*v + v^2 + thetax*v)
    
    non_zero_indices <- which(Aold[m,] != 0)
    #AvgXconnection is muI and AvgYconnection is muJ
    x[2, i] <- alpha * x[1, i] + (1 - alpha) * muI[m] + (muI[m] - mean(muJ[non_zero_indices])) * gamma1 + rnorm(1) * xix
    
    
    
    # speciation event - which occurs with probability pX
    if (runif(1) < pX) {
      NsppX <- NsppX + 1  # keeps track of how many spp there are now
      
      
      if (NsppX > maxNX) {
        cat("error, the number of species type X is greater than the number allocated\n")
        toobig <- toobig + 1
        break
      }
      
      # add new spp trait
      x[2, NsppX] <- x[1, i] + rnorm(1) * xis
      
      #add a new row for the new X species
      A <- rbind(A, A[m, ])  # inherits parental connections
      M <- rbind(M, M[m, ])  # and those connections inherit the same fitness value, at least initially
      
      
      # now we make sure that we know that this new species is a sister species to species i
      #boo <- which(phylogenyX[1, ] == i)
      #if((NsppX-1)>=(boo[1]+1)){
      #  for (j in seq((NsppX-1),(boo[1]+1),-1)) {
      #    phylogenyX <- cbind(phylogenyX,phylogenyX[, j])
      #  }
      #}
      #if((boo[1]+1)<=dim(phylogenyX)[2]){
      #  phylogenyX[, boo[1]+1] <- c(NsppX, n)
      #} else {phylogenyX<-cbind(phylogenyX, c(NsppX, n))}
      inter_event_times<-c(inter_event_times, Sys.time()-last_event_time)
      nt_time<-Sys.time()
    }
    
    
  }   
  
  m <- 0
  NoldsppY <- NsppY
  
  for (i in iYextant) {
    
    m <- m + 1; #counts which species we are on
    mJ<- sum(Aold[,m])

    thetaJ <- thetax / mJ  # CLT
    
    beta <- (thetaJ^2 + thetaJ*v + v^2) / (thetaJ^2 + thetaJ*v + v^2 + thetay*v)
    gamma2 <- thetaJ * thetax / (thetaJ^2 + thetaJ*v + v^2 + thetay*v)
    
    non_zero_indices <- which(Aold[,m] != 0)
    #AvgXconnection is muI and AvgYconnection is muJ
    y[2, i] <- beta * y[1, i] + (1 - beta) * muJ[m] + (muJ[m] - mean(muI[non_zero_indices])) * gamma2 + rnorm(1) * xix
    
    
    # speciation event - which occurs with probability pY
    if (runif(1) < pY) {
      NsppY <- NsppY + 1  # keeps track of how many spp there are now
     
      
      if (NsppY > maxNY) {
        cat("error, the number of species type Y is greater than the number allocated\n")
        toobig <- toobig + 1
        break
      }
      
      # add new spp trait
      y[2, NsppY] <- y[1, i] + rnorm(1) * xis
      
      #add a column for the new y spp
      A <- cbind(A, A[, m])  # inherits parental connections
      M <- cbind(M, M[, m])  # and those connections inherit the same fitness value, at least initially
      
      # now we make sure that we know that this new species is a sister species to species i
     # boo <- which(phylogenyY[1, ] == i)
      #if((NsppY-1)>=boo[1]){
      #  for (j in (NsppY-1):boo[1]) {
      #    phylogenyY <- cbind(phylogenyY,phylogenyY[, j])
      #  }
      #}
      #if((boo[1]+1)<=dim(phylogenyY)[2]){
      #  phylogenyY[, boo[1]+1] <- c(NsppY, n)
      #} else {phylogenyY<-cbind(phylogenyY, c(NsppY, n))}
      inter_event_times<-c(inter_event_times, Sys.time()-last_event_time)
      last_event_time<-Sys.time()
    }
    
  }
  
  #interaction matrix - these are in the order in which spp appeared, but not including extinct species 
  
  if((NoldsppX+1)<=NsppX){
    iXextantnew <- c(iXextant,(NoldsppX+1):NsppX)#give the lineages of X that are extant
    } else {
    iXextantnew<-iXextant
    }
  
  
  if((NoldsppY+1)<=NsppY){
    iYextantnew <- c(iYextant,(NoldsppY+1):NsppY) #give the linages of Y that are extant
  } else {
      iYextantnew<-iYextant
      }
  
  Anew <- karray(0, c(length(iXextantnew),length(iYextantnew)))
  
  #count<-1
  im<-0
  jm<-0
  
  for (i in iXextantnew) {
    im<-im+1
    for (j in iYextantnew) {
      jm<-jm+1
      matching <- c*A[im,jm]+ (1-c)*M[im,jm]
      
      if(matching>runif(1)){
        Anew[im, jm]<-1
      }
    }
    jm<-0
  }
  
  #counter for extinctions(species death)
  Xextinctions<-Xextinctions+length(which(rowSums(Anew) == 0))
  Yextinctions<-Yextinctions+length(which(colSums(Anew) == 0)) 
  
  # Identify extant species with connections
  #we now want to eliminate all species that have no connections to
  #anyone else
  #To look for rows of 0 do a sum(A') then a find
  XextantA <- which(rowSums(Anew) != 0) #these are all the x species that have 
  # at least one connection maintained to someone else
  iXextant <- iXextantnew[XextantA]
  NextantsppX <- length(iXextant)
  
  
  YextantA <- which(colSums(Anew) != 0)
  iYextant <- iYextantnew[YextantA]
  NextantsppY <- length(iYextant)
  
  # Check for extinction of species
  if (NsppX == 0 && NsppY == 0) {
    cat("extinction of both species\n")
    extinctions <- extinctions + 1
    break # replaces MATLAB's break in this context
    # note - next will skip an interation
    # we want break because it will stop the whole loop
  } else if (NsppX == 0) {
    cat("extinction of species X\n")
    extinctions <- extinctions + 1
    break
  } else if (NsppY == 0) {
    cat("extinction of species Y\n")
    extinctions <- extinctions + 1
    break
  }
  
  
  
  # Update interaction matrix
  A <- karray(Anew[XextantA, YextantA], c(NextantsppX, NextantsppY))
  
  # Update traits for next generation
  x[1, ] <- x[2, ]
  x[2, ] <- rep(NaN, maxNX)
  y[1, ] <- y[2, ]
  y[2, ] <- rep(NaN, maxNY)
  
  # Calculate connectedness
  #connectedness[1, n] <- sum(sum(A)) / (NextantsppX * NextantsppY)

## appending new interaction matrix into the list
ts_list[[k]][[n]]<-as.array(A)
   
if(dim(as.array(A))[1]>1 &&dim(as.array(A))[2]>1){
  modu_scores<-c(modu_scores, computeModules(as.array(A))@likelihood)
}
else{modu_scores<-c(modu_scores, NA)}

ts_stats[, n]<-c(networklevel(as.array(A), index ="info"), networklevel(as.array(A), index = c("nestedness", "cluster coefficient")))


end_time<-Sys.time()
  #recording time interval for each interations
  iteration_times[n]<-end_time-start_time
}
ts_stats_list[[k]]<-ts_stats
modu_scores_list[[k]]<-modu_scores
inter_event_times<-inter_event_times[-1]
}

```











## Visualize the bipartite graph at the last time stamp

``` {r}
A<-ts_list[[3]][[600]]
# assign plants' name to the plants
rname_vec<-rep(0, length(A[,1]))
for (i in 1:length(A[,1])) {
  rname_vec[i]<-paste("PL",i,sep = "")
}
row.names(A)<-rname_vec

cname_vec<-rep(0, length(A[1,]))
for (i in 1:length(A[1,])) {
  cname_vec[i]<-paste("V",i,sep = "")
}
row.names(A)<-rname_vec
colnames(A)<-cname_vec
# view the new matrix
View(A)

```

### First convert incidence matrix to edgelist
```{r}
#
polli.g<- graph.incidence(A, weighted = TRUE)
polli_el <- get.edgelist(polli.g)
View(polli_el)
```



### Structuring the bipartite graphs
```{r}
# Set the arbitrary char as webID 
webID <- data.frame(matrix("pp", nrow = nrow(polli_el), ncol = 1))
polli_new <- cbind(polli_el, webID)
# assign column names
colnames(polli_new)<- c("plant", "pollinator", "webID")
View(polli_new)
```



### Plotting network interactions between two node types
```{r}
#Generate the network matrix in bipartite
polli_web<- frame2webs(polli_new, varnames = c("plant", "pollinator", "webID"), type.out = "list", emptylist = TRUE)
# create a color vector
cols1<-c( '#8214a0', '#005ac8', '#00a0fa', '#fa78fa', '#14d2dc', '#aa0a3c', '#fa7850', '#0ab45a', '#f0f032', '#a0fa82', '#fae6be') 
# plot the two-dimensional matrix to a bipartite graph
plotweb(polli_web$"pp", method='cca', labsize=1, col.interaction=cols1, bor.col.interaction=cols1)                    
```




### Visualizing the interaction matrix
This code will visualize the interaction/adjacency matrix. Look up the documentation, play with the command, and then comment within the code block to explain how to use visweb.

``` {r warning=FALSE}
# # set the color of levels of interactions
# cols2<-c('white', '#006e82')
# #you can also try other palettes
cols2 <- brewer.pal(2, "Reds")
# #visualize the interaction matrix
par(mfrow=c(2,2))
plot(1:T, xall[1:T,1], type="p", cex=0.5, xlab = "iterations", ylab="Mean Trait x", main="Evolution of Species Trait X")
plot(1:T, yall[1:T,1], type="p", cex=0.5, xlab="iterations", ylab="Mean Trait y", main="Evolution of Species Trait Y")
plotweb(polli_web$"pp", method='cca', labsize=1, col.interaction=cols1, bor.col.interaction=cols1)        
visweb(polli_web$'pp', type='nested', labsize=0.3, plotsize=28 ,square="def",def.col=cols2)
```

## Now we are considering time-evolving features


### constructing a multidimensional array from list of interaction matrices
```{r}
#largest dimension
max_dim<-unlist(lapply(ts_list, dim))[c(n*2-1, n*2)]
#building a multidimensional array with with incomplete entries
ts_list_expanded<-list()
for (i in 1:n) {
  new_mat<-matrix(NA,nrow=max_dim[1],ncol=max_dim[2])
  new_mat[1:nrow(ts_list[[i]]), 1:ncol(ts_list[[i]])] <- ts_list[[i]]
  ts_list_expanded[[i]]<-new_mat
}
ts_multi_A<-array(c(unlist(ts_list_expanded)), dim = c(max_dim[1], max_dim[2], n))
```


### Key time-series statistics 

```{r, warning=FALSE}
par(mfrow= c(5, 2), mar = c(4.5, 4, 1, 2))

for(q in 1: length(modu_scores_list)){
plot(modu_scores_list[[q]], type = "l", ylab="Modularity score", xlab="Iterations")#, main="modularity over time")
}

```

# ```{r old visuals}
# plot(1:T, xall[1:T,1], type="p", cex=0.5, ylab="Mean Trait x", main="Evolution of Species Trait X")
# plot(1:T, yall[1:T,1], type="p", cex=0.5, ylab="Mean Trait y", main="Evolution of Species Trait Y")
# 
# x.at<-seq(0, NsppX+1)
# y.at<-seq(0, NsppY+1)
# 
# # image(t(A[1:NsppX, 1:(NsppY-1)]), axes=FALSE, main="Adjacency Matrix of Interactions", xlab="Pollinator species", ylab="Plant species")
# ```


```{r connectance}

# Plot the evolution of species traits over time for X and Y
#par(mfrow=c(3,1))  # Set up a 3x2 plotting grid
# 
# plot(1:T, xall[1:T,1], type="p", cex=0.5, ylab="Mean Trait x", main="Evolution of Species Trait X")
# plot(1:T, yall[1:T,1], type="p", cex=0.5, ylab="Mean Trait y", main="Evolution of Species Trait Y")
# 

 #Display the adjacency matrix of interactions(this is t=400)
# x.at<-seq(0, NsppX+1)
# y.at<-seq(0, NsppY+1)
# image(t(A[1:NsppX, 1:(NsppY-1)]), axes=FALSE, main="Adjacency Matrix of Interactions", xlab="Pollinator species", ylab="Plant species")
# axis(1, at=x.at)
# axis(2, at=y.at)

    
# Display the distribution of connections per pollinator
# hist(rowSums(as.array(A[1:NsppX, 1:(NsppY-1)])), main="Distribution of Connections per Pollinator", xlab="Number of connections", ylab="Frequency") 

# Display connectedness and several key indices over time
# plot(1:T, connectedness, type="l", ylab="Connectedness", xlab="Iterations", main="Connectedness Over Time")
rownames(ts_stats_list[[1]])<-c("connectance", "web asymmetry", "links per species", "number of compartments", "number of species hl", "number of species ll", "clustering coefficient", "nestedness", "clustering coefficient hl", "clustering coefficient ll")
par(mfrow= c(5, 2), mar = c(4.5, 4, 1, 2))

for (i in 1:length(ts_stats_list[[1]][,1])) {
  plot(1:T, ts_stats_list[[i]][1,1:T], type = "l", ylab = rownames(ts_stats_list[[1]])[1], xlab = "Iterations")
}



# plot(inter_event_times, type = "l", ylab="inter_event_times", xlab="Iterations", main="Inter-event Times")
# plot(iteration_times, type = "l", ylab="inter_interation_times", xlab="Iterations", main="Inter-iteration Times Over Time")

```



```{r web asymmetry}
rownames(ts_stats_list[[2]])<-c("connectance", "web asymmetry", "links per species", "number of compartments", "number of species hl", "number of species ll", "clustering coefficient", "nestedness", "clustering coefficient hl", "clustering coefficient ll")#, "modularity")
par(mfrow= c(5, 2), mar = c(4.5, 4, 1, 2))

for (i in 1:length(ts_stats_list[[2]][,1])) {
  plot(1:T, ts_stats_list[[i]][2,1:T], type = "l", ylab = rownames(ts_stats_list[[2]])[2], xlab = "Iterations")
}



```



```{r links per species}
rownames(ts_stats_list[[3]])<-c("connectance", "web asymmetry", "links per species", "number of compartments", "number of species hl", "number of species ll", "clustering coefficient", "nestedness", "clustering coefficient hl", "clustering coefficient ll")#, "modularity")
par(mfrow= c(5, 2), mar = c(4.5, 4, 1, 2))

for (i in 1:length(ts_stats_list[[3]][,1])) {
  plot(1:T, ts_stats_list[[i]][3,1:T], type = "l", ylab = rownames(ts_stats_list[[3]])[3], xlab = "Iterations")
}
```

```{r number of compartments}
rownames(ts_stats_list[[4]])<-c("connectance", "web asymmetry", "links per species", "number of compartments", "number of species hl", "number of species ll", "clustering coefficient", "nestedness", "clustering coefficient hl", "clustering coefficient ll")#, "modularity")

for (i in 1:length(ts_stats_list[[4]][,1])) {
  plot(1:T, ts_stats_list[[i]][4,1:T], type = "l", ylab = rownames(ts_stats_list[[4]])[4], xlab = "Iterations")
}

```

```{r number of s hl}
rownames(ts_stats_list[[5]])<-c("connectance", "web asymmetry", "links per species", "number of compartments", "number of species hl", "number of species ll", "clustering coefficient", "nestedness", "clustering coefficient hl", "clustering coefficient ll")#, "modularity")

for (i in 1:length(ts_stats_list[[5]][,1])) {
  plot(1:T, ts_stats_list[[i]][5,1:T], type = "l", ylab = rownames(ts_stats_list[[5]])[5], xlab = "Iterations")
}


```


```{r}
rownames(ts_stats_list[[6]])<-c("connectance", "web asymmetry", "links per species", "number of compartments", "number of species hl", "number of species ll", "clustering coefficient", "nestedness", "clustering coefficient hl", "clustering coefficient ll")#, "modularity")

for (i in 1:length(ts_stats_list[[6]][,1])) {
  plot(1:T, ts_stats_list[[i]][6,1:T], type = "l", ylab = rownames(ts_stats_list[[6]])[6], xlab = "Iterations")
}

```


```{r}
rownames(ts_stats_list[[7]])<-c("connectance", "web asymmetry", "links per species", "number of compartments", "number of species hl", "number of species ll", "clustering coefficient", "nestedness", "clustering coefficient hl", "clustering coefficient ll")#, "modularity")

par(mfrow= c(5, 2), mar = c(4.5, 4, 1, 2))

for (i in 1:length(ts_stats_list[[7]][,1])) {
  plot(1:T, ts_stats_list[[i]][7,1:T], type = "l", ylab = rownames(ts_stats_list[[7]])[7], xlab = "Iterations")
}

```


```{r}


```


```{r}
rownames(ts_stats_list[[7]])<-c("connectance", "web asymmetry", "links per species", "number of compartments", "number of species hl", "number of species ll", "clustering coefficient", "nestedness", "clustering coefficient hl", "clustering coefficient ll")
for (i in 1:length(ts_stats_list[[9]][,1])) {
  plot(1:T, ts_stats_list[[i]][9,1:T], type = "l", ylab = rownames(ts_stats_list[[7]])[9], xlab = "Iterations")
}
```


```{r}
rownames(ts_stats_list[[7]])<-c("connectance", "web asymmetry", "links per species", "number of compartments", "number of species hl", "number of species ll", "clustering coefficient", "nestedness", "clustering coefficient hl", "clustering coefficient ll")
for (i in 1:length(ts_stats_list[[7]][,1])) {
  plot(1:T, ts_stats_list[[i]][10,1:T], type = "l", ylab = rownames(ts_stats_list[[7]])[10], xlab = "Iterations")
}
```




### time-series analysis

```{r}

date <- seq(Sys.Date(), by = "days", length.out = 600)


sample_1<-as.data.frame(t(ts_stats_list[[1]]))
sample_1<-as_tibble(cbind(date, modu_scores_list[[i]], sample_1))
colnames(sample_1)<-c("date", "modularity","connectance", "web asymmetry", "links per species", "number of compartments", "number of species hl", "number of species ll", "clustering coefficient", "nestedness", "clustering coefficient hl", "clustering coefficient ll")


```


#### data tibble convertion
```{r}
sample_list<-list()
for (i in 1:10) {
  
  sample_list[[i]]<-as.data.frame(t(ts_stats_list[[i]]))
  sample_list[[i]]<-as_tibble(cbind(date, modu_scores_list[[i]], sample_list[[i]]))
  # assign(paste("sample_", i,sep = ""), as.tibble(cbind(date,modu_scores_list[[i]],assign(paste("sample_", i,sep = ""),as.data.frame((t(ts_stats_list[[i]])))))))
  colnames(sample_list[[i]])<-c("date", "modularity","connectance", "web asymmetry", "links per species", "number of compartments", "number of species hl", "number of species ll", "clustering coefficient", "nestedness", "clustering coefficient hl", "clustering coefficient ll")
}

  # rownames(glue(sample_{i}))<-c("date", "modularity","connectance", "web asymmetry", "links per species", "number of compartments", "number of species hl", "number of species ll", "clustering coefficient", "nestedness", "clustering coefficient hl", "clustering coefficient ll")

#sample_1<-as.data.frame(t(ts_stats_list[[1]]))
#sample_1<-as_tibble(cbind(date, sample_1))
```

#### data export
```{r}
for (i in 1:10) {
  sample_list[[i]]$modularity[which(is.na(sample_list[[i]]$modularity))]<-0

  write_csv(sample_list[[i]], paste("indicators_sample",i,".csv", sep = ""))
}
```



#### Anomalize Package

```{r}
sample_1 %>%
    time_decompose(connectance, method = "twitter") %>%
    anomalize(remainder, method = "gesd") %>%
    time_recompose() %>%    
    plot_anomaly_decomposition()
```
```{r}
sample1_conn_anomalized<-sample_1 %>% time_decompose(connectance, method = "twitter") %>% anomalize(remainder, method = "gesd")
which(sample1_conn_anomalized$anomaly=="Yes")
```


```{r}
sample_1$modularity[which(is.na(sample_1$modularity))]<-0

sample_1 %>%
    time_decompose(modularity, method = "twitter") %>%
    anomalize(remainder, method = "gesd") %>%
    time_recompose() %>%    
    plot_anomalies(time_recomposed = TRUE, ncol = 3, alpha_dots = 0.25)
```


```{r}
sample_1 %>%
    time_decompose(`clustering coefficient`, method = "twitter") %>%
    anomalize(remainder, method = "gesd") %>%
    time_recompose() %>%    
    plot_anomalies(time_recomposed = TRUE, ncol = 3, alpha_dots = 0.25)
```

```{r}
#sample_1_decomposed<-sample_1 %>% time_decompose(connectance, method = "twitter")

sample_list_decomposed<-list()
for (i in 1:10) {
  
  sample_list_decomposed[[i]]<-sample_list[[i]] %>% time_decompose(connectance, method = "stl")
  
  write_csv(sample_list_decomposed[[i]], paste("Connectance_sample",i,"_decomposed.csv", sep = ""))
}

```


